---
title: "Likelihood Ratios Method"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
```

*Reference Paper: Broadie, M. and Glasserman, P. (1996). Estimating security price derivatives using simulation, Management Science 42, 269–285.*

# 1. European Call Options on Dividend Paying Assets

## Likelihood Ratio method (w/o control variates)

> List #1.

The Likelihood ratio estimators:
$$                      
Vega(\frac{dp}{d\sigma}) = e^{-rT}\max(S_T - K,0)(-d*\frac{\partial d}{\partial\sigma}- \frac{1}{\sigma}) \notag\\ 
Delta(\frac{dp}{dS_0}) = e^{-rT}\max(S_T - K, 0)\frac{1}{S_0\sigma^2T}\times(ln(\frac{S_T}{S_0})-(r-\delta-\frac{1}{2}\sigma^2)T) \notag\\
Gamma(\frac{d^2p}{dS_0^2}) = e^{-rT}\max(S_T - K, 0)\frac{d^2-d\sigma\sqrt{T}-1}{S_0^2\sigma^2T} \notag\\
Rho(\frac{dp}{dr}) = e^{-rT}\max(S_T - K, 0)(-T+\frac{d\sqrt{T}}{\sigma}) \notag\\              
Theta(-\frac{dp}{dT}) = e^{-rT}\max(S_T - K, 0)(r+d\frac{\partial d}{\partial T} + \frac{1}{2T}) \notag\\
$$

Where $S_T \text{ is given by } S_T = S_{t_i}= S_0e^{(r-\delta-\frac{\sigma^2}{2})T+\sigma\sqrt{T}Z_i}\text{with } Z_i\text{ a random standard normal distributed for i = 1,...,n}$ and by inversion we are approximating standard normal $Z_i$ by $\Phi^{-1}(U_i)$ with $U_i \sim i.i.d.Unifrom(0,1)$ random uniform over domain on (0,1). ($\Phi^{-1}(\cdot)$ is the CDF of standard normal distribution)

And $\frac{\partial d}{\partial\sigma}$, $d$, and $\frac{\partial d}{\partial T}$ are given by
$$
\frac{\partial d}{\partial\sigma} = (ln(\frac{S_0}{S_T})+(r-\delta+\frac{1}{2}\sigma^2)T)/(\sigma^2\sqrt{T})\notag\\
d = d(S_T) = (ln(\frac{S_T}{S_0})-(r-\delta-\frac{1}{2}\sigma^2)T)/(\sigma\sqrt{T})\notag\\
\frac{\partial d}{\partial T} = (-ln(\frac{S_T}{S_0})-(r-\delta-\frac{1}{2}\sigma^2)T)/(2\sigma^2T^{3/2})\notag
$$

Thus, the simulation estimator for price of the European Call option with dividend paying assets is given by 
$$\hat{C}_{re} = \frac{1}{n}\sum_{i=1}^ne^{-rT}\max(S_{t_i}-K,0)$$ where, 
$$S_{t_i} = S_0e^{(r-\delta-\frac{\sigma^2}{2})T-\sigma\sqrt{T}\Phi^{-1}(U_i)}$$ in this case, by inversion we are approximating standard normal Z by $\Phi^{-1}(U_i)$ with $U_i \sim i.i.d.Unifrom(0,1)$ random uniform over domain on (0,1).

And the estimator for $Delta$ using the Pathwise method for example is
$$
\begin{align}
\hat{Delta}_{LR} &= \frac{1}{n}\sum_{i=1}^n e^{-rT}\max(S_{t_i} - K, 0)\frac{1}{S_0\sigma^2T}\times(ln(\frac{S_{t_i}}{S_0})-(r-\delta-\frac{1}{2}\sigma^2)T)\notag
\end{align}
$$
depending on parameter of interest from **List #1.**.

**Define function for estimating European Call options derivatives using Likelihood ratio method under BS model**

variables                      output 
--------------------           -----------------------------------
n: # of simulations            hat_LR: the estimated derivatives of an European call option using Likelihood Ratio
S0: the spot price             hat_LR_std_err: the standard error for estimating the derivatives of an European call option using Likelihood Ratio
r: the rate of return
sigma: volatility              
T: maturity date
K: strike price
delta: dividend
input: 'delta', 'vega',etc...

```{r}
Likelihood <- function(n, S0, r, sigma, T, K, delta, input)
{
  # create length n random normal vector before simulations
  zi = qnorm(runif(n,0,1))
  
  # create derivatives to store the estimated Greeks at each simulation
  derivatives = matrix(0,n,1)
  
  # the stock simulated at one run
  stock = S0 * exp((r - delta - sigma^2/2)*T 
                            + sigma * sqrt(T) * zi)
  
  if(input == 'delta')
  {
    # gives estimate for delta
    derivatives = exp(-r*T)*pmax(stock-K,0)*1/(S0*sigma^2*T)*
                  (log(stock/S0)-(r-delta-1/2*sigma^2)*T)
    # determine the estimator for delta of a plain call option
    hat_LR = sum(derivatives)/n
    
    # determine the standard error of the estimator
    hat_LR_std_err = sqrt(var(derivatives)/n)
    
    # return the desire output
    return(c(hat_LR, hat_LR_std_err))
    
  }else if (input == 'vega'){
    # define d
    d = (log(stock/S0)-(r-delta-1/2*sigma^2)*T)/(sigma*sqrt(T))
    # define d(d)/d(sigma)
    d_sigma = (log(S0/stock)+(r-delta+1/2*sigma^2)*T)/(sigma^2*sqrt(T))
    
    # gives estimate for vega
    derivatives = exp(-r*T) *pmax(stock-K,0)*(-d*d_sigma-1/sigma)
    
    # determine the estimator for vega of a plain call option
    hat_LR = sum(derivatives)/n
    
    # determine the standard error of the estimator
    hat_LR_std_err = sqrt(var(derivatives)/n)
    
    # return the desire output
    return(c(hat_LR, hat_LR_std_err))
  
  }else if (input == 'gamma'){
    # define d
    d = (log(stock/S0)-(r-delta-1/2*sigma^2)*T)/(sigma*sqrt(T))
    
    # gives estimate for gamma
    derivatives = exp(-r*T) *pmax(stock-K,0)*(d^2-d*sigma*sqrt(T)-1)/
                  (S0^2*sigma^2*T)
    
    # determine the estimator for gamma of a plain call option
    hat_LR = sum(derivatives)/n
    
    # determine the standard error of the estimator
    hat_LR_std_err = sqrt(var(derivatives)/n)
    
    # return the desire output
    return(c(hat_LR, hat_LR_std_err))
    
  }else if (input == 'rho'){
    # define d
    d = (log(stock/S0)-(r-delta-1/2*sigma^2)*T)/(sigma*sqrt(T))
    
    # gives estimate for rho
    derivatives = exp(-r*T) *pmax(stock-K,0)*(-T+d*sqrt(T)/sigma)
    
    # determine the estimator for rho of a plain call option
    hat_LR = sum(derivatives)/n
    
    # determine the standard error of the estimator
    hat_LR_std_err = sqrt(var(derivatives)/n)
    
    # return the desire output
    return(c(hat_LR, hat_LR_std_err))
    
  }else if (input == 'theta'){
    # define d
    d = (log(stock/S0)-(r-delta-1/2*sigma^2)*T)/(sigma*sqrt(T))
    
    # define d(d)/d(T)
    d_T = (-log(stock/S0)-(r-delta-1/2*sigma^2)*T)/(2*sigma*T^(3/2))
    
    # gives estimate for theta for each simulation
    derivatives = exp(-r*T) *pmax(stock-K,0)*(r+d*d_T+1/(2*T))
      
    # determine the estimator for theta of a plain call option
    hat_LR = sum(derivatives)/n
    
    # determine the standard error of the estimator
    hat_LR_std_err = sqrt(var(derivatives)/n)
    
    # return the desire output
    return(c(hat_LR, hat_LR_std_err))
    
  }else{
    cat('Please type in the proper name of the derivative! e.g. delta, gamma etc.')
  }
}
```

**initialized variables as the article suggested**
```{r}
# set variables
n = 10000 # simulation tuns
# S0 = 110
# S0 = 110
S0 = 110
r = 0.1
K = 100 
delta = 0.03
sigma = 0.25
T = 0.2
```

**$Delta$**
```{r}
set.seed(123)
ptm <- proc.time()
result =  Likelihood(n, S0, r, sigma, T, K, delta, 'delta')
proc.time() - ptm
Delta_re = result[1]
Delta_re_Std_err = result[2]

result = cbind(mean(Delta_re), mean(Delta_re_Std_err))
colnames(result) = c('Delta uisng Likelihood Ratio Method', 'Std Err')
kable(result)
```

**$Vega$**

```{r}
set.seed(123)
ptm <- proc.time()

result =  Likelihood(n, S0, r, sigma, T, K, delta, 'vega')
proc.time() - ptm
Vega_re = result[1]
Vega_re_Std_err = result[2]

result = cbind(mean(Vega_re), mean(Vega_re_Std_err))
colnames(result) = c('Vega uisng Likelihood Ratio Method', 'Std Err')
kable(result)
```

**$Gamma$**
```{r}
set.seed(123)
ptm <- proc.time()

result =  Likelihood(n, S0, r, sigma, T, K, delta, 'gamma')
proc.time() - ptm
Gamma_re = result[1]
Gamma_re_Std_err = result[2]

result = cbind(mean(Gamma_re), mean(Gamma_re_Std_err))
colnames(result) = c('Gamma uisng Likelihood Ratio Method', 'Std Err')
kable(result)
```

**$Rho$**

```{r}
set.seed(123)
ptm <- proc.time()

result =  Likelihood(n, S0, r, sigma, T, K, delta, 'rho')
proc.time() - ptm
Rho_re = result[1]
Rho_re_Std_err = result[2]

result = cbind(mean(Rho_re), mean(Rho_re_Std_err))
colnames(result) = c('Rho uisng Likelihood Ratio Method', 'Std Err')
kable(result)
```

**$Theta$**

```{r}
set.seed(123)
ptm <- proc.time()

result =  Likelihood(n, S0, r, sigma, T, K, delta, 'theta')
proc.time() - ptm
Theta_re = result[1]
Theta_re_Std_err = result[2]

result = cbind(mean(Theta_re), mean(Theta_re_Std_err))
colnames(result) = c('Theta uisng Likelihood Ratio Method', 'Std Err')
kable(result)
```

## Likelihood Ratio method (w control variates)

For consistency, we use the same control variate, the terminal security price, for European call option example. (and so as for Asian Call option and Stochastic volatility options)


We denote the unbiased simulation estimator of the derivatives as $D$, specifically the exact Likelihood Ratio estimators defined as before. i.e. ($Vega(\frac{dp}{d\sigma})$,$Delta(\frac{dp}{dS_0})$ etc.)


That is, d = E[D], where d is the true value of derivative to be estimated. We consider letting $S_T$ represent the simulated terminal underlying price of the security. Since E[$S_T$] = $e^{(r-\delta)T}S_0$, as for $ln(\frac{S_T}{S0})\sim N((r-\delta-\frac{\sigma^2}{2})T,\sigma^2T)$, then $exp(ln(\frac{S_T}{S0})) = \frac{S_T}{S0}$ has a log normal distribution with mean $E[\frac{S_T}{S0}] = e^{((r-\delta-\frac{\sigma^2}{2})T+(\sigma \sqrt{T})^2/2)} = e^{(r-\delta)T}$ i.e.E[$S_T$] = $e^{(r-\delta)T}S_0$


Thus, to estimate E[D], we have found a r.v. $S_T$ correlated with D and such that $\sum_{i=1}^n\frac{S_T}{n} = E[S_T]$ is known. Then, we can obtained an unbiased estimator of derivative using control variate:

$$
D' = \frac{1}{n}\sum_{i=1}^{n}D_i+\beta(S_{T_i}-e^{(r-\delta)T}S_0)
$$
where $D_i$ are the unbiased Liklihood Ratio estimators for the derivatives at each n simulations and $S_{T_i} = S_0e^{(r-\delta-\frac{\sigma^2}{2})T+\sigma\sqrt{T}Z_i}\text{with } Z_i\text{ a random standard normal distributed for i = 1,...,n}$ and by inversion we are approximating standard normal $Z_i$ by $\Phi^{-1}(U_i)$ with $U_i \sim i.i.d.Unifrom(0,1)$ random uniform over domain on (0,1). ($\Phi^{-1}(\cdot)$ is the CDF of standard normal distribution)


In this case, $\beta$ can be chosen to minimized $Var(D')$ i.e. $\min_{\beta}(Var(D'))$ so that if the estimator D are regressed on $S_T$, the slope of the regression line solves the minimization problem, i.e. want to find $\beta$ that minmized $Var(D')$

$$
\begin{align}
\frac{\partial}{\partial\beta}Var(D') &= \frac{\partial}{\partial\beta}[\frac{(Var(D))^2}{n}+\frac{\beta^2}{n}Var(S_T)-\frac{2\beta}{n}Cov(D,S_T)]\notag\\
&=\frac{2\beta}{n}Var(S_T)-\frac{2}{n}Cov(D,S_T) = 0 \notag\\
&\Rightarrow \beta^* = \frac{Cov(D,ST)}{Var(S_T)}
\end{align}
$$
where $Var(D)$ is the sample variance of the simulation using the Liklihood Ratio estimator i.e. $Var(D) = \frac{1}{n-1}\sum_{i=1}^{n}(D_i - \hat{D})^2$ and one can check it's a minimum: $\frac{\partial^2Var(D')}{\partial\beta^2} = \frac{2}{n}Var(S_T) \geq 0$ (Concave upward, min exists).

**Define function for estimating European Call options derivatives using Liklihood Ratio method under BS model with control variate**

variables                      output 
--------------------           -----------------------------------
n: # of simulations            hat_path_cv: the estimated derivatives of an European call option using Liklihood Ratio method with CV method
S0: the spot price             hat_path_cv_std_err: the standard error for estimating the derivatives of an European call option using Liklihood Ratio method with CV method
r: the rate of return
sigma: volatility              
T: maturity date
K: strike price
delta: dividend
input: 'delta', 'vega',etc...

```{r}
Likelihood_cv<- function(n, S0, r, sigma, T, K, delta, input)
{
  # define E[S_T] as S_T_i
  S_T_i = S0 * exp((r - delta)*T)
  
  # create length n random normal vector before simulations
  zi = qnorm(runif(n,0,1))
  
  # create derivatives to store the estimated Greeks at each simulation
  derivatives = matrix(0,n,1)
  
  # the stock simulated at one run
  stock = S0 * exp((r - delta - sigma^2/2)*T 
                            + sigma * sqrt(T) * zi)
  
  if(input == 'delta')
  {
    # gives estimate for delta
    derivatives = exp(-r*T)*pmax(stock-K,0)*1/(S0*sigma^2*T)*
                  (log(stock/S0)-(r-delta-1/2*sigma^2)*T)
    # estimate beta
    beta = c(cov(derivatives, stock)/ var(stock))
    
    # apply control variates to the method
    derivatives_cv = derivatives + beta*(S_T_i - stock)
    
    # determine the estimator for delta of a plain call option
    hat_LR_cv = sum(derivatives_cv)/n
    
    # determine the standard error of the estimator
    hat_LR_cv_std_err = sqrt(var(derivatives_cv)/n)
    
    # return the desire output
    return(c(hat_LR_cv, hat_LR_cv_std_err))
    
  }else if (input == 'vega'){
    # define d
    d = (log(stock/S0)-(r-delta-1/2*sigma^2)*T)/(sigma*sqrt(T))
    # define d(d)/d(sigma)
    d_sigma = (log(S0/stock)+(r-delta+1/2*sigma^2)*T)/(sigma^2*sqrt(T))
    
    # gives estimate for vega
    derivatives = exp(-r*T) *pmax(stock-K,0)*(-d*d_sigma-1/sigma)
    
    # estimate beta
    beta = c(cov(derivatives, stock)/ var(stock))
    
    # apply control variates to the method
    derivatives_cv = derivatives + beta*(S_T_i - stock)
    
    # determine the estimator for delta of a plain call option
    hat_LR_cv = sum(derivatives_cv)/n
    
    # determine the standard error of the estimator
    hat_LR_cv_std_err = sqrt(var(derivatives_cv)/n)
    
    # return the desire output
    return(c(hat_LR_cv, hat_LR_cv_std_err))
  
  }else if (input == 'gamma'){
    # define d
    d = (log(stock/S0)-(r-delta-1/2*sigma^2)*T)/(sigma*sqrt(T))
    
    # gives estimate for gamma
    derivatives = exp(-r*T) *pmax(stock-K,0)*(d^2-d*sigma*sqrt(T)-1)/
                  (S0^2*sigma^2*T)
    
    # estimate beta
    beta = c(cov(derivatives, stock)/ var(stock))
    
    # apply control variates to the method
    derivatives_cv = derivatives + beta*(S_T_i - stock)
    
    # determine the estimator for delta of a plain call option
    hat_LR_cv = sum(derivatives_cv)/n
    
    # determine the standard error of the estimator
    hat_LR_cv_std_err = sqrt(var(derivatives_cv)/n)
    
    # return the desire output
    return(c(hat_LR_cv, hat_LR_cv_std_err))
    
  }else if (input == 'rho'){
    # define d
    d = (log(stock/S0)-(r-delta-1/2*sigma^2)*T)/(sigma*sqrt(T))
    
    # gives estimate for rho
    derivatives = exp(-r*T) *pmax(stock-K,0)*(-T+d*sqrt(T)/sigma)
    
    # estimate beta
    beta = c(cov(derivatives, stock)/ var(stock))
    
    # apply control variates to the method
    derivatives_cv = derivatives + beta*(S_T_i - stock)
    
    # determine the estimator for delta of a plain call option
    hat_LR_cv = sum(derivatives_cv)/n
    
    # determine the standard error of the estimator
    hat_LR_cv_std_err = sqrt(var(derivatives_cv)/n)
    
    # return the desire output
    return(c(hat_LR_cv, hat_LR_cv_std_err))
    
  }else if (input == 'theta'){
    # define d
    d = (log(stock/S0)-(r-delta-1/2*sigma^2)*T)/(sigma*sqrt(T))
    
    # define d(d)/d(T)
    d_T = (-log(stock/S0)-(r-delta-1/2*sigma^2)*T)/(2*sigma*T^(3/2))
    
    # gives estimate for theta for each simulation
    derivatives = exp(-r*T) *pmax(stock-K,0)*(r+d*d_T+1/(2*T))
      
    # estimate beta
    beta = c(cov(derivatives, stock)/ var(stock))
    
    # apply control variates to the method
    derivatives_cv = derivatives + beta*(S_T_i - stock)
    
    # determine the estimator for delta of a plain call option
    hat_LR_cv = sum(derivatives_cv)/n
    
    # determine the standard error of the estimator
    hat_LR_cv_std_err = sqrt(var(derivatives_cv)/n)
    
    # return the desire output
    return(c(hat_LR_cv, hat_LR_cv_std_err))
    
  }else{
    cat('Please type in the proper name of the derivative! e.g. delta, gamma etc.')
  }
}
```

**$Delta with control variate$**

```{r}
set.seed(123)
ptm <- proc.time()
proc.time() - ptm
result =  Likelihood_cv(n, S0, r, sigma, T, K, delta, 'delta')
Delta_re = result[1]
Delta_re_Std_err = result[2]

result = cbind(mean(Delta_re), mean(Delta_re_Std_err))
colnames(result) = c('Delta uisng Likelihood Ratio Method with CV', 'Std Err')
kable(result)
```

**$Vega with control variate$**

```{r}
set.seed(123)
ptm <- proc.time()
result =  Likelihood_cv(n, S0, r, sigma, T, K, delta, 'vega')
proc.time() - ptm
Vega_re = result[1]
Vega_re_Std_err = result[2]

result = cbind(mean(Vega_re), mean(Vega_re_Std_err))
colnames(result) = c('Vega uisng Likelihood Ratio Method with CV', 'Std Err')
kable(result)
```

**$Gamma with control variate$**

```{r}
set.seed(123)
ptm <- proc.time()
result =  Likelihood_cv(n, S0, r, sigma, T, K, delta, 'gamma')
proc.time() - ptm
Gamma_re = result[1]
Gamma_re_Std_err = result[2]

result = cbind(mean(Gamma_re), mean(Gamma_re_Std_err))
colnames(result) = c('Gamma uisng Likelihood Ratio Method with CV', 'Std Err')
kable(result)
```

**$Rho with control variate$**

```{r}
set.seed(123)
ptm <- proc.time()

result =  Likelihood_cv(n, S0, r, sigma, T, K, delta, 'rho')
proc.time() - ptm
Rho_re = result[1]
Rho_re_Std_err = result[2]

result = cbind(mean(Rho_re), mean(Rho_re_Std_err))
colnames(result) = c('Rho uisng Likelihood Ratio Method with CV', 'Std Err')
kable(result)
```

**$Theta with control variate$**

```{r}
set.seed(123)
ptm <- proc.time()
result =  Likelihood_cv(n, S0, r, sigma, T, K, delta, 'theta')
proc.time() - ptm
Theta_re = result[1]
Theta_re_Std_err = result[2]

result = cbind(mean(Theta_re), mean(Theta_re_Std_err))
colnames(result) = c('Theta uisng Likelihood Ratio Method with CV', 'Std Err')
kable(result)
```

## Exact Value of Greeks

$$
\begin{align}
Delta(\frac{dp}{dS_0}) &= e^{-\delta T}N(d_1(K))\notag\\
Vega(\frac{dp}{d\sigma}) &= \sqrt{T}e^{-\delta T}S_0n(d_1(K))\notag\\
Gamma(\frac{d^2p}{dS_0^2}) &= e^{-\delta T}\frac{n(d_1(K))}{S_0\sigma\sqrt{T}}\notag\\
Rho(\frac{dp}{dr}) &= KTe^{-rT}N(d_2(K))\notag\\
Theta(-\frac{dp}{dT}) &= -\frac{\sigma e^{-\delta T}S_0n(d_1(K))}{2\sqrt{T}}+\delta e^{-\delta T}S_0N(d_1(K)) - rKe^{-rT}N(d_2(K))\notag
\end{align}
$$
Where, 
$$
d_1(x) = \frac{[ln(\frac{S_0}{x}) + (r-\delta+\frac{1}{2}\sigma^2)T]}{\sigma\sqrt{T}} = -d(x) + \sigma\sqrt{T},
$$
and $d_2 = -d(x)$, $N(\cdot)$ is the culmulative distribution function of a standard normal random variables and $n(\cdot)$ is the density function of the standard normal
**initialized some common used variables**
```{r}
d1 = (log(S0/K) + (r - delta + 1/2*sigma^2)*T)/(sigma*sqrt(T))
d = sigma*sqrt(T) - d1
d2 = -d
```


```{r, warning = FALSE}
delta_exact = exp(-delta*T)*pnorm(d1)
vega_exact = sqrt(T)*exp(-delta*T)*S0*dnorm(d1)
gamma_exact = exp(-delta*T)*dnorm(d1)/(S0*sigma*sqrt(T))
rho_exact = K*T*exp(-r*T)*pnorm(d2)
theta_exact = (-sigma*exp(-delta*T)*S0*dnorm(d1))/(2*sqrt(T)) +
              delta*exp(-delta*T)*S0*pnorm(d1) - r*K*exp(-r*T)*pnorm(d2)

result = rbind(delta_exact, vega_exact, gamma_exact, rho_exact, theta_exact)
rownames(result) = c('Exact delta', 'Exact vega', 'Exact gamma', 'Exact rho', 'Exact theta')
kable(result)
```


# 2. Asian Call Options

## Likelihood Ratio method (w/o control variates)

> List #2.

The Likelihood ratio estimators:
$$                      
Vega(\frac{dp}{d\sigma}) = e^{-rT}\max(\bar{S} - K,0)\sum_{i=1}^m(-d_i*\frac{\partial d_i}{\partial\sigma}- \frac{1}{\sigma}) \notag\\ 
Delta(\frac{dp}{dS_0}) = e^{-rT}\max(\bar{S} - K,0)\frac{1}{S_0\sigma^2\Delta t_1}\times(ln(\frac{S_1}{S_0})-(r-\delta-\frac{1}{2}\sigma^2)\Delta t_1) \notag\\
Gamma(\frac{d^2p}{dS_0^2}) = e^{-rT}\max(\bar{S} - K,0)\frac{d_1^2-d_1\sigma\sqrt{\Delta t_1}-1}{S_0^2\sigma^2\Delta t_1} \notag\\
Rho(\frac{dp}{dr}) = e^{-rT}\max(\bar{S} - K,0)(-T+\sum_{i=1}^m\frac{d_i\sqrt{\Delta t_i}}{\sigma}) \notag\\              
Theta(-\frac{dp}{dT}) = e^{-rT}\max(\bar{S} - K,0)(r+d_1\frac{\partial d_1}{\partial T} + \frac{1}{2\Delta t_1}) \notag\\
$$
**Define function for estimating Asian Call options derivatives using LR method under BS model**

variables                      output 
--------------------           -----------------------------------
n: # of simulations            hat_A_LR: the estimated derivatives of an Asian call option using LR method
S0: the spot price             hat_A_LR_std_err: the standard error for estimating the derivatives of an Asian call option using LR method
r: the rate of return
sigma: volatility              
T: maturity date
K: strike price
delta: dividend
input: 'delta', 'vega',etc...
s: the last s days 

```{r}
LR_A <- function(n, S0, r, sigma, T, K, delta, input,s)
{
  # create payoff
  C = matrix(0,n,1)
  
  # create length n random normal vector before simulations
  zi = matrix(qnorm(runif(n*s,0,1)),ncol=s,nrow=n)
  
  # create derivatives to store the estimated Greeks at each simulation
  derivatives = matrix(0,n,1)
  
  # create tj for each increment of last few days
  t_j = c(T - (s-1)/365.25, rep(1/365.25, s-1))
  
  # build function for d_i
  d_i <- function(S, S_1, delta_t_i)
  {
    return((log(S/S_1)-(r-delta-sigma^2/2)*delta_t_i)/(sigma*sqrt(delta_t_i)))
  }
  # build function for d(d_i)/d(sigma)
  partial_d_i <- function(S, S_1, delta_t_i)
  {
    return((log(S_1/S)+(r-delta+sigma^2/2)*delta_t_i)/(sigma^2*sqrt(delta_t_i)))
  }
  
  if(input == 'delta')
  {
    # start the simulation
    for(i in 1:n)
    {
      # define matrix that store the stock price along the path
      stock = matrix(0,s+1,1)
      
      # initialized with spot price
      stock[1] = S0
      
      # calculate the stock price in each path
      for(j in 2:(s+1))
      {
        # generate stock price for each simulation
        stock[j] = stock[j-1]* 
          exp((r - delta - sigma^2/2) * t_j[j-1] + sigma * sqrt(t_j[j-1]) * zi[i,j-1])
      }
      # gives estimate for delta for each simulation
      derivatives[i] = exp(-r*T)*max(mean(stock[2:(s+1)])-K,0) * 1/(S0*sigma^2*t_j[1]) *
                       (log(stock[2]/S0) - (r-delta-sigma^2/2)*t_j[1])
    }
    hat_A_LR = sum(derivatives)/n
    
    # determine the standard error of the estimator
    hat_A_LR_std_err = sqrt(var(derivatives)/n)
    
    # return the desire output
    return(c(hat_A_LR, hat_A_LR_std_err))
    
  }else if (input == 'vega'){
    # start the simulation
    for(i in 1:n)
    {
      # define matrix that store the stock price along the path
      stock = matrix(0,s+1,1)
      
      # initialized with spot price
      stock[1] = S0
      
      # calculate the stock price in each path
      for(j in 2:(s+1))
      {
        # generate stock price for each simulation
        stock[j] = stock[j-1]* 
          exp((r - delta - sigma^2/2) * t_j[j-1] + sigma * sqrt(t_j[j-1]) * zi[i,j-1])
      }
      # gives estimate for vega for each simulation
      derivatives[i] = exp(-r*T)*max(mean(stock[2:(s+1)])-K,0)*
                       sum(-d_i(stock[2:nrow(stock)], stock[1:(nrow(stock)-1)], t_j)*
                           partial_d_i(stock[2:nrow(stock)], stock[1:(nrow(stock)-1)], t_j)-
                             1/sigma)
    }
    hat_A_LR = sum(derivatives)/n
    
    # determine the standard error of the estimator
    hat_A_LR_std_err = sqrt(var(derivatives)/n)
    
    # return the desire output
    return(c(hat_A_LR, hat_A_LR_std_err))
  
  }else if (input == 'gamma'){
    # start the simulation
    for(i in 1:n)
    {
      # define matrix that store the stock price along the path
      stock = matrix(0,s+1,1)
      
      # initialized with spot price
      stock[1] = S0
      
      # calculate the stock price in each path
      for(j in 2:(s+1))
      {
        # generate stock price for each simulation
        stock[j] = stock[j-1]* 
          exp((r - delta - sigma^2/2) * t_j[j-1] + sigma * sqrt(t_j[j-1]) * zi[i,j-1])
      }
      # define d_1
      d_1 = (log(stock[2]/stock[1]) - (r-delta-sigma^2/2)*t_j[1])/(sigma*sqrt(t_j[1]))
      
      # gives estimate for gamma for each simulation
      derivatives[i] = exp(-r*T)*max(mean(stock[2:(s+1)])-K,0)*
                      ((d_1^2 - d_1*sigma*sqrt(t_j[1])-1)/
                         (S0^2*sigma^2*t_j[1]))
    }
    hat_A_LR = sum(derivatives)/n
    
    # determine the standard error of the estimator
    hat_A_LR_std_err = sqrt(var(derivatives)/n)
    
    # return the desire output
    return(c(hat_A_LR, hat_A_LR_std_err))    
  }else if (input == 'rho'){
    # start the simulation
    for(i in 1:n)
    {
      # define matrix that store the stock price along the path
      stock = matrix(0,s+1,1)
      
      # initialized with spot price
      stock[1] = S0
      
      # calculate the stock price in each path
      for(j in 2:(s+1))
      {
        # generate stock price for each simulation
        stock[j] = stock[j-1]* 
          exp((r - delta - sigma^2/2) * t_j[j-1] + sigma * sqrt(t_j[j-1]) * zi[i,j-1])
      }
      # gives estimate for rho for each simulation
      derivatives[i] = exp(-r*T)*max(mean(stock[2:(s+1)])-K,0)*
                       (-T + sum(d_i(stock[2:nrow(stock)], stock[1:(nrow(stock)-1)], t_j)*
                                   sqrt(t_j)/sigma))
    }
    hat_A_LR = sum(derivatives)/n
    
    # determine the standard error of the estimator
    hat_A_LR_std_err = sqrt(var(derivatives)/n)
    
    # return the desire output
    return(c(hat_A_LR, hat_A_LR_std_err))
    
  }else if (input == 'theta'){
    # start the simulation
    for(i in 1:n)
    {
      # define matrix that store the stock price along the path
      stock = matrix(0,s+1,1)
      
      # initialized with spot price
      stock[1] = S0
      
      # calculate the stock price in each path
      for(j in 2:(s+1))
      {
        # generate stock price for each simulation
        stock[j] = stock[j-1]* 
          exp((r - delta - sigma^2/2) * t_j[j-1] + sigma * sqrt(t_j[j-1]) * zi[i,j-1])
      }
      # define d(d_1)/dT
      d_1_dT = (-log(stock[2]/stock[1]) - (r-delta-sigma^2/2)*t_j[1])/(2*sigma*t_j[1]^(3/2))
      
      # gives estimate for rho for each simulation
      derivatives[i] = exp(-r*T)*max(mean(stock[2:(s+1)])-K,0)*
                       (r + d_i(stock[2], stock[1], t_j[1]) *
                          d_1_dT + 1/(2*t_j[1]))
    }
    hat_A_LR = sum(derivatives)/n
    
    # determine the standard error of the estimator
    hat_A_LR_std_err = sqrt(var(derivatives)/n)
    
    # return the desire output
    return(c(hat_A_LR, hat_A_LR_std_err))
    
  }else{
    cat('Please type in the proper name of the derivative! e.g. delta, gamma etc.')
  }
}
```

**initialized variables as the article suggested**
```{r}
# set variables
n = 10000 # simulation tuns
# S0 = 110
# S0 = 110
S0 = 110
r = 0.1
K = 100 
delta = 0.03
sigma = 0.25
T = 0.2
s = 30
```

**$Delta$**

```{r}
set.seed(123)

#tic()
ptm <- proc.time()
result =  LR_A(n, S0, r, sigma, T, K, delta, 'delta',s)
proc.time() - ptm
#toc()
Delta_re = result[1]
Delta_re_Std_err = result[2]

result = cbind(mean(Delta_re), mean(Delta_re_Std_err))
colnames(result) = c('Delta of Asian Call Opiton uisng Pathwise Method', 'Std Err')
kable(result)
```

**$Vega$**

```{r}
set.seed(123)
ptm <- proc.time()

result =  LR_A(n, S0, r, sigma, T, K, delta, 'vega',s)
proc.time() - ptm
Vega_re = result[1]
Vega_re_Std_err = result[2]

result = cbind(mean(Vega_re), mean(Vega_re_Std_err))
colnames(result) = c('Vega of Asian Call Opiton uisng Pathwise Method', 'Std Err')
kable(result)
```

**$Gamma$**

```{r}
set.seed(123)
ptm <- proc.time()

result =  LR_A(n, S0, r, sigma, T, K, delta, 'gamma',s)
proc.time() - ptm
Gamma_re = result[1]
Gamma_re_Std_err = result[2]

result = cbind(mean(Gamma_re), mean(Gamma_re_Std_err))
colnames(result) = c('Gamma of Asian Call Opiton uisng Pathwise Method', 'Std Err')
kable(result)
```

**$Rho$**

```{r}
set.seed(123)
ptm <- proc.time()

result =  LR_A(n, S0, r, sigma, T, K, delta, 'rho',s)
proc.time() - ptm
Rho_re = result[1]
Rho_re_Std_err = result[2]

result = cbind(mean(Rho_re), mean(Rho_re_Std_err))
colnames(result) = c('Rho of Asian Call Opiton uisng Pathwise Method', 'Std Err')
kable(result)
```

**$Theta$**

```{r}
set.seed(123)
ptm <- proc.time()

result =  LR_A(n, S0, r, sigma, T, K, delta, 'theta', s)
proc.time() - ptm
Theta_re = result[1]
Theta_re_Std_err = result[2]

result = cbind(mean(Theta_re), mean(Theta_re_Std_err))
colnames(result) = c('Theta of Asian Call Opiton uisng Pathwise Method', 'Std Err')
kable(result)
```

## Likelihood Ratio method (w control variates)

**Define function for estimating Asian Call options derivatives using LR method with CV under BS model**

variables                      output 
--------------------           -----------------------------------
n: # of simulations            hat_A_LR_cv: the estimated derivatives of an Asian call option using Pathwise method with CV
S0: the spot price             hat_A_LR_cv_std_err: the standard error for estimating the derivatives of an Asian call option using Pathwise method with CV
r: the rate of return
sigma: volatility              
T: maturity date
K: strike price
delta: dividend
input: 'delta', 'vega',etc...
s: the last s days 

```{r}
LR_A_CV <- function(n, S0, r, sigma, T, K, delta, input,s)
{
  # create payoff
  C = matrix(0,n,1)
  
  # create length n random normal vector before simulations
  zi = matrix(qnorm(runif(n*s,0,1)),ncol=s,nrow=n)
  
  # create derivatives to store the estimated Greeks at each simulation
  derivatives = matrix(0,n,1)
  
  # create tj for each increment of last few days
  t_j = c(T - (s-1)/365.25, rep(1/365.25, s-1))
  
  # define E[S_T] as S_T_i
  S_T_i = S0 * exp((r - delta)*T)
  
  # define matrix for storing the terminal stock price at each n
  S_T = matrix(0,n,1)
  
  # build function for d_i
  d_i <- function(S, S_1, delta_t_i)
  {
    return((log(S/S_1)-(r-delta-sigma^2/2)*delta_t_i)/(sigma*sqrt(delta_t_i)))
  }
  # build function for d(d_i)/d(sigma)
  partial_d_i <- function(S, S_1, delta_t_i)
  {
    return((log(S_1/S)+(r-delta+sigma^2/2)*delta_t_i)/(sigma^2*sqrt(delta_t_i)))
  }
  
  if(input == 'delta')
  {
    # start the simulation
    for(i in 1:n)
    {
      # define matrix that store the stock price along the path
      stock = matrix(0,s+1,1)
      
      # initialized with spot price
      stock[1] = S0
      
      # calculate the stock price in each path
      for(j in 2:(s+1))
      {
        # generate stock price for each simulation
        stock[j] = stock[j-1]* 
          exp((r - delta - sigma^2/2) * t_j[j-1] + sigma * sqrt(t_j[j-1]) * zi[i,j-1])
      }
      # gives estimate for delta for each simulation
      derivatives[i] = exp(-r*T)*max(mean(stock[2:(s+1)])-K,0) * 1/(S0*sigma^2*t_j[1]) *
                       (log(stock[2]/S0) - (r-delta-sigma^2/2)*t_j[1])
      # store terminal stock price at each n simulation
      S_T[i] = stock[s+1]
    }
    # estimate beta
    beta = c(cov(derivatives, S_T)/ var(S_T))
    
    # apply control variates to the method
    derivatives_cv = derivatives + beta*(S_T_i - S_T)
    
    # determine the estimator for delta of a plain call option
    hat_A_LR_cv = sum(derivatives_cv)/n
    
    # determine the standard error of the estimator
    hat_A_LR_cv_std_err = sqrt(var(derivatives_cv)/n)
    
    # return the desire output
    return(c(hat_A_LR_cv, hat_A_LR_cv_std_err))
    
  }else if (input == 'vega'){
    # start the simulation
    for(i in 1:n)
    {
      # define matrix that store the stock price along the path
      stock = matrix(0,s+1,1)
      
      # initialized with spot price
      stock[1] = S0
      
      # calculate the stock price in each path
      for(j in 2:(s+1))
      {
        # generate stock price for each simulation
        stock[j] = stock[j-1]* 
          exp((r - delta - sigma^2/2) * t_j[j-1] + sigma * sqrt(t_j[j-1]) * zi[i,j-1])
      }
      # gives estimate for vega for each simulation
      derivatives[i] = exp(-r*T)*max(mean(stock[2:(s+1)])-K,0)*
                       sum(-d_i(stock[2:nrow(stock)], stock[1:(nrow(stock)-1)], t_j)*
                           partial_d_i(stock[2:nrow(stock)], stock[1:(nrow(stock)-1)], t_j)-
                             1/sigma)
      # store terminal stock price at each n simulation
      S_T[i] = stock[s+1]
    }
    # estimate beta
    beta = c(cov(derivatives, S_T)/ var(S_T))
    
    # apply control variates to the method
    derivatives_cv = derivatives + beta*(S_T_i - S_T)
    
    # determine the estimator for delta of a plain call option
    hat_A_LR_cv = sum(derivatives_cv)/n
    
    # determine the standard error of the estimator
    hat_A_LR_cv_std_err = sqrt(var(derivatives_cv)/n)
    
    # return the desire output
    return(c(hat_A_LR_cv, hat_A_LR_cv_std_err))
  
  }else if (input == 'gamma'){
    # start the simulation
    for(i in 1:n)
    {
      # define matrix that store the stock price along the path
      stock = matrix(0,s+1,1)
      
      # initialized with spot price
      stock[1] = S0
      
      # calculate the stock price in each path
      for(j in 2:(s+1))
      {
        # generate stock price for each simulation
        stock[j] = stock[j-1]* 
          exp((r - delta - sigma^2/2) * t_j[j-1] + sigma * sqrt(t_j[j-1]) * zi[i,j-1])
      }
      # define d_1
      d_1 = (log(stock[2]/stock[1]) - (r-delta-sigma^2/2)*t_j[1])/(sigma*sqrt(t_j[1]))
      
      # gives estimate for gamma for each simulation
      derivatives[i] = exp(-r*T)*max(mean(stock[2:(s+1)])-K,0)*
                      ((d_1^2 - d_1*sigma*sqrt(t_j[1])-1)/
                         (S0^2*sigma^2*t_j[1]))
      # store terminal stock price at each n simulation
      S_T[i] = stock[s+1]
    }
    # estimate beta
    beta = c(cov(derivatives, S_T)/ var(S_T))
    
    # apply control variates to the method
    derivatives_cv = derivatives + beta*(S_T_i - S_T)
    
    # determine the estimator for delta of a plain call option
    hat_A_LR_cv = sum(derivatives_cv)/n
    
    # determine the standard error of the estimator
    hat_A_LR_cv_std_err = sqrt(var(derivatives_cv)/n)
    
    # return the desire output
    return(c(hat_A_LR_cv, hat_A_LR_cv_std_err)) 
  }else if (input == 'rho'){
    # start the simulation
    for(i in 1:n)
    {
      # define matrix that store the stock price along the path
      stock = matrix(0,s+1,1)
      
      # initialized with spot price
      stock[1] = S0
      
      # calculate the stock price in each path
      for(j in 2:(s+1))
      {
        # generate stock price for each simulation
        stock[j] = stock[j-1]* 
          exp((r - delta - sigma^2/2) * t_j[j-1] + sigma * sqrt(t_j[j-1]) * zi[i,j-1])
      }
      # gives estimate for rho for each simulation
      derivatives[i] = exp(-r*T)*max(mean(stock[2:(s+1)])-K,0)*
                       (-T + sum(d_i(stock[2:nrow(stock)], stock[1:(nrow(stock)-1)], t_j)*
                                   sqrt(t_j)/sigma))
      # store terminal stock price at each n simulation
      S_T[i] = stock[s+1]
    }
    # estimate beta
    beta = c(cov(derivatives, S_T)/ var(S_T))
    
    # apply control variates to the method
    derivatives_cv = derivatives + beta*(S_T_i - S_T)
    
    # determine the estimator for delta of a plain call option
    hat_A_LR_cv = sum(derivatives_cv)/n
    
    # determine the standard error of the estimator
    hat_A_LR_cv_std_err = sqrt(var(derivatives_cv)/n)
    
    # return the desire output
    return(c(hat_A_LR_cv, hat_A_LR_cv_std_err))
    
  }else if (input == 'theta'){
    # start the simulation
    for(i in 1:n)
    {
      # define matrix that store the stock price along the path
      stock = matrix(0,s+1,1)
      
      # initialized with spot price
      stock[1] = S0
      
      # calculate the stock price in each path
      for(j in 2:(s+1))
      {
        # generate stock price for each simulation
        stock[j] = stock[j-1]* 
          exp((r - delta - sigma^2/2) * t_j[j-1] + sigma * sqrt(t_j[j-1]) * zi[i,j-1])
      }
      # define d(d_1)/dT
      d_1_dT = (-log(stock[2]/stock[1]) - (r-delta-sigma^2/2)*t_j[1])/(2*sigma*t_j[1]^(3/2))
      
      # gives estimate for rho for each simulation
      derivatives[i] = exp(-r*T)*max(mean(stock[2:(s+1)])-K,0)*
                       (r + d_i(stock[2], stock[1], t_j[1]) *
                          d_1_dT + 1/(2*t_j[1]))
      # store terminal stock price at each n simulation
      S_T[i] = stock[s+1]
    }
    # estimate beta
    beta = c(cov(derivatives, S_T)/ var(S_T))
    
    # apply control variates to the method
    derivatives_cv = derivatives + beta*(S_T_i - S_T)
    
    # determine the estimator for delta of a plain call option
    hat_A_LR_cv = sum(derivatives_cv)/n
    
    # determine the standard error of the estimator
    hat_A_LR_cv_std_err = sqrt(var(derivatives_cv)/n)
    
    # return the desire output
    return(c(hat_A_LR_cv, hat_A_LR_cv_std_err))
    
  }else{
    cat('Please type in the proper name of the derivative! e.g. delta, gamma etc.')
  }
}
```

**initialized variables as the article suggested**
```{r}
# set variables
n = 10000 # simulation tuns
# S0 = 110
# S0 = 110
S0 = 110
r = 0.1
K = 100 
delta = 0.03
sigma = 0.25
T = 0.2
s = 30
```

**$Delta$**

```{r}
set.seed(123)

#tic()
ptm <- proc.time()
result =  LR_A_CV(n, S0, r, sigma, T, K, delta, 'delta',s)
proc.time() - ptm
#toc()
Delta_re = result[1]
Delta_re_Std_err = result[2]

result = cbind(mean(Delta_re), mean(Delta_re_Std_err))
colnames(result) = c('Delta of Asian Call Opiton uisng Likelihood Method with CV', 'Std Err')
kable(result)
```

**$Vega$**

```{r}
set.seed(123)
ptm <- proc.time()

result =  LR_A_CV(n, S0, r, sigma, T, K, delta, 'vega',s)
proc.time() - ptm
Vega_re = result[1]
Vega_re_Std_err = result[2]

result = cbind(mean(Vega_re), mean(Vega_re_Std_err))
colnames(result) = c('Vega of Asian Call Opiton uisng Likelihood Method with CV', 'Std Err')
kable(result)
```

**$Gamma$**

```{r}
set.seed(123)
ptm <- proc.time()

result =  LR_A_CV(n, S0, r, sigma, T, K, delta, 'gamma',s)
proc.time() - ptm
Gamma_re = result[1]
Gamma_re_Std_err = result[2]

result = cbind(mean(Gamma_re), mean(Gamma_re_Std_err))
colnames(result) = c('Gamma of Asian Call Opiton uisng Likelihood Method with CV', 'Std Err')
kable(result)
```

**$Rho$**

```{r}
set.seed(123)
ptm <- proc.time()

result =  LR_A_CV(n, S0, r, sigma, T, K, delta, 'rho',s)
proc.time() - ptm
Rho_re = result[1]
Rho_re_Std_err = result[2]

result = cbind(mean(Rho_re), mean(Rho_re_Std_err))
colnames(result) = c('Rho of Asian Call Opiton uisng Likelihood Method with CV', 'Std Err')
kable(result)
```

**$Theta$**

```{r}
set.seed(123)
ptm <- proc.time()

result =  LR_A_CV(n, S0, r, sigma, T, K, delta, 'theta', s)
proc.time() - ptm
Theta_re = result[1]
Theta_re_Std_err = result[2]

result = cbind(mean(Theta_re), mean(Theta_re_Std_err))
colnames(result) = c('Theta of Asian Call Opiton uisng Likelihood Method with CV', 'Std Err')
kable(result)
```
